---
title: "2. Project"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidygraph)
library(sfnetworks)
library(tidyverse)
library(sf)
library(tmap)

tmap_mode("view")

berlinstraßen <- st_read("edge_berlin3.csv", crs = 31468)
acc <- read.csv("acc.csv")
unfaelle <- read.csv2("Unfaelle.csv")
bezirke <- st_read("shp-bezirke/bezirke_berlin.shp")

```

Berlin-Network
======

Row 
-----------------------------------------------------------------------

### edges
```{r}
valueBox(86785, icon = "fa-road")
```

### nodes
```{r}
valueBox(36954, icon = "fa-circle")
```

### edges per node
```{r}
gauge(2.35, min = 1, max = 6)
```

Row 
-----------------------------------------------------------------------

### Berlin centrality base

Shows the centrality of the Berlin network with no given weight, filtered by used streets over 20*10^6.

```{r}

with_centrality <- as_sfnetwork(berlinstraßen) %>%
  activate(edges) %>%
  mutate(centrality = centrality_edge_betweenness()) %>%
  filter(centrality > 20000000)

tm_shape(st_as_sf(with_centrality, "edges")) + 
  tm_lines(col = "centrality", size = "centrality", scale = 3,breaks = c(20000000,40000000,60000000,80000000,100000000,120000000))

```


### Berlin centrality length

Shows the centrality of the Berlin network with weight = length, filtered by used streets over 20*10^6.

```{r}

berlinstraßen$length <- as.numeric(berlinstraßen$length)

with_centrality <- as_sfnetwork(berlinstraßen) %>%
  activate(edges) %>%
  mutate(centrality = centrality_edge_betweenness(weights = length)) %>%
  filter(centrality > 20000000)

tm_shape(st_as_sf(with_centrality, "edges")) + 
  tm_lines(col = "centrality", size = "centrality", scale = 3)

```

### Berlin counts

Shows the usage of the Berlin network from the open-Berlin-scenario, filtered by streets over 20.000 vehicles a day .

```{r}

berlinstraßen$count <- as.numeric(berlinstraßen$count)
berlinstraßen_count <- filter(berlinstraßen, count > 20000)

tm_shape(berlinstraßen_count) +
  tm_lines(col = "count", scale = 3,breaks = c(20000,40000,60000,80000,100000,120000))

```

### Berlin centrality with time

Shows the centrality of the Berlin network with weight = length/speed, filtered by used streets over 20*10^6.

```{r}

berlinstraßen$speed <- as.numeric(berlinstraßen$speed)
berlinstraßen$length <- as.numeric(berlinstraßen$length)

with_centrality_speed <- as_sfnetwork(berlinstraßen) %>%
  activate(edges) %>%
  mutate(centrality = centrality_edge_betweenness(weights = length/speed)) %>%
  filter(centrality > 20000000)

tm_shape(st_as_sf(with_centrality_speed, "edges")) + 
  tm_lines(col = "centrality", size = "centrality", scale = 3, breaks = c(20000000,40000000,60000000,80000000,100000000,250000000))
```

Row {data-height=30}
-----------------------------------------------------------------------

### Notes:

1. The data used can be found at: <https://svn.vsp.tu-berlin.de/repos/public-svn/matsim/scenarios/countries/de/berlin/berlin-v5.5-10pct/>.
2. The calculation was carried out with the entire data set, but the network was filtered for the visualization.

Accidents 
==========

Row 
-----------------------------------------------------------------------

### accident rate

```{r}

berlinstraßen$count <- as.numeric(berlinstraßen$count)
berlinstraßen$length <- as.numeric(berlinstraßen$length)
berlinstraßen$id <- as.numeric(berlinstraßen$id)

unfaellepoint <- st_as_sf(unfaelle, coords = c("XGCSWGS84", "YGCSWGS84"), crs = 4326)
unfaellepoint <- st_transform(unfaellepoint, crs = 31468)

berlinstraßen_acc <- left_join(berlinstraßen, acc, by = "id")
berlinstraßen_acc <- filter(berlinstraßen_acc, !is.na(acc))
berlinstraßen_acc <- mutate(berlinstraßen_acc, "accident rate" = (1000000*acc)/(365*count*length))
berlinstraßen_acc$"accident rate" <- as.numeric(berlinstraßen_acc$"accident rate")
berlinstraßen_acc <- filter(berlinstraßen_acc, "accident rate" > 0)
berlinstraßen_acc <- filter(berlinstraßen_acc, !is.na("accident rate"))

tm_shape(berlinstraßen_acc) +
  tm_lines(col = "accident rate", scale = 3, breaks = c(0,0.25,0.5,1,2,5,10))

```

### costs per neighborhoood, 2019

```{r}

unfaellepoint <- st_as_sf(unfaelle, coords = c("XGCSWGS84", "YGCSWGS84"), crs = 4326)

bezirke <- st_transform(bezirke,crs =  4326)

unfaellepoint <- mutate(unfaellepoint, costs = if_else("UKATEGORIE"==1,1035165,if_else("UKATEGORIE"==2,110506,4403)) )

joined_data <- st_join(bezirke, unfaellepoint)

accident_summary <- joined_data %>%
  group_by(SCHLUESSEL) %>%
  summarize(num_accidents=sum(costs))

tm_shape(accident_summary) +
  tm_polygons(col = "num_accidents", title = "accident costs in millions per year") +
  tm_text("num_accidents", size = 0.9)

```

Row {data-height=20}
-----------------------------------------------------------------------

### source

<https://www.bast.de/BASt_2017/DE/Publikationen/Foko/2011-2010/2010-17.html>
